Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-05-09 WholePlotTrajectories.Rmd
M&M

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973].

These three indices belong to the set of HCDT or generalized entropy, respectively corresponding to the 0, 1 and 2 order of diversity (q), which proved well suited for diversity studies [@Patil1982;@Tothmeresz1995]. 
The functional diversity was reported using the Rao index of quadratic entropy which combines species abundance distribution and average pairwise dissimilarity based on all functional and life traits.

>>>>

The taxonomic diversity was assessed through Richness and the Hill number translation of Shannon and Simpson indices [@Hill1973].
These three indices belong to the set of HCDT or generalized entropy, respectively corresponding to the 0, 1 and 2 order of diversity (q), which proved well suited for diversity studies [@Patil1982;@Tothmeresz1995]. 
The functional diversity was reported using the Rao index of quadratic entropy which combines species abundance distribution and average pairwise dissimilarity based on all functional and life traits.

The functional redundancy was measured as the overlap among species in communities' functional space.
The samples of the trait database were first located with a PCA analysis in a two-dimensional functional space summarizing the 8 functional traits considered.
Then, multivariate kernel density estimator associated with individual trees were summed to give the distribution of traits probabilites of each species.
For each community the trait probability distributions of corresponding species were combined and weighted by species abundance. 
Eventually communities functional redundancy was measured as the sum of overlap between species weighted functional density.
